Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-08 draft.tex
poisson

Recently, a generalization of the concept of the enveloping algebra of a Lie algebra has emerged: 
each dg Lie algebra $\fg$ has an enveloping $\EE_n$ algebra $\UU_n\fg$, for every $n$, 
so that $\UU_1\fg$ is the usual enveloping algebra $U\fg$. 
Building on prior work \cite{BD, AF} [Owen's thesis?], 
Knudsen \cite{Knudsen} developed these ideas extensively and offered a useful factorization algebra model for the enveloping $\EE_n$ algebra. 
Our central goal here is to generalize the some well-known results about the enveloping algebra $U\fg$ to $\UU_n\fg$, for all $n$, such as
\begin{enumerate}
\item[(1)] the (underived) center of $U\sl_{N+1}$ is isomorphic to $(\Sym(\CC^{N}))^{S_N}$, where $\CC^{N}$ denotes the Cartan subalgebra of $\sl_{N+1}$ and $S_N$ is the Weyl group of $SL_{N+1}$, and
\item[(2)] the derived center of the enveloping algebra $U\fg$ is given by derived invariants of the adjoint action of $\fg$ on $U\fg$. That is to say $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$.
\end{enumerate}
\owen{And keep going}
%
%Our results pertains to (1) by taking $N \to \infty$, and to (2) through the derived {\em centralizer} of the map $\UU_n\sl_\infty \hookrightarrow \UU_n\gl_\infty(A)$, where $A$ is a dg algebra. Note that the usual derived center is the centralizer of the identity map $\UU_n\fg \to \UU_n\fg$.
%
%We will review these notions and describe our results in detail Min the next section. When $n=1$,  \owen{state the classical thing here!}
%
%Our primary tool here is the Loday-Quillen-Tsygan (LQT) theorem which describes the large $N$ limit of the Lie algebra homology of $\gl_N(A)$, for a dg associative algebra $A$. Since the enveloping $\EE_n$ algebra of a Lie algebra can be constructed as a locally constant factorization algebra made out of the shifted Chevalley-Eilenberg chains \cite{}, the relevance of the LQT theorem in this context  should be apparent. From this point of view, one can think of our main result as an $\EE_n$ generalization of the LQT theorem. We hope these ideas have exciting applications in quantum field theory and random matrix theory, as well as to other large $N$ limit phenomena.

@@

See section~\ref{sec: en background} for a brief discussion of $\EE_n$ algebras and their relationship with locally constant factorization algebras on $\RR^n$, section~\ref{sec: enveloping} for a brief discussion of the enveloping $\EE_n$ algebra construction, and see section~\ref{sec: centralizer} 
for a brief discussion about centralizers to maps of $\EE_n$ algebras.

@@

Even to state our central result, we need to review a few results and terminology.
First, our basic context is $\EE_n$ algebras.
By $\EE_n$ we mean any operad or colored operad or $\infty$-operad equivalent to the topological operad of little $n$-disks in $\RR^n$, where the notion of equivalence is in some appropriate $\infty$-categorical setting of operads. 
In particular, we will require that its $\infty$-category of algebras in $\Ch_k^{\otimes_k}$ agree with those of the little $n$-disks operad. 
For us the preferred presentation is by locally constant factorization algebras on $\RR^n$,
which, as we explain below, can be understood via a colored operad whose colors are open sets in~$\RR^n$.

Many notions from ordinary algebra admit natural generalizations to $\EE_n$ algebras.
For instance, to each Lie algebra $\fg$ (and more generally $L_\infty$ algebra),
there is an {\em enveloping $\EE_n$ algebra} $\UU_n \fg$, thanks to \cite{Knudsen}.
Similarly, every $\EE_n$ algebra $A$ has a {\em center} ${\frak Z}_n(A)$, which is an $E_{n+1}$ algebra and hence more commutative than~$A$.
More generally, for any map of $\EE_n$ algebras $f: A \to B$, there is a {\em centralizer} ${\frak Z}_n(f)$, 
which is a generalization of the commutant.
We review these notions more fully in Section~\ref{sec: background}.

Our work here relies on a concrete and convenient model for these enveloping $\EE_n$ algebras by factorization algebras.
In particular, thanks again to \cite{Knudsen}, 
we know that the $\EE_n$ enveloping algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
There is another factorization algebra whose underlying assigns $\clies(\Omega^*(V) \otimes \fg)$ to each open~$V$.
Our paper shows that such factorization algebras model other important $\EE_n$ algebras, notably centralizers.

\begin{thm}
\label{thm: centralizer}
Let $\fg$ and $\fh$ be $L_\infty$ algebras over the real or complex numbers, 
and let $f: \fg \rightsquigarrow \fh$ be a homotopy-coherent morphism of $L_\infty$ algebras
(i.e., a map of conilpotent cocommutative coalgebras $f: \cliels(\fg) \to \cliels(\fh)$).
This map determines functorially a map of $\EE_n$ algebras
\[
\UU_n f: \UU_n \fg \to \UU_n \fh
\]
between their enveloping $\EE_n$ algebras.
The centralizer of this map ${\frak Z}_n(\UU_n f)$ is an $\EE_n$-algebra modeled by the factorization algebra 
\[
\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh)_f)
\]
equipped with a convolution-type product,
where the subscript $f$ indicates how $\cliels(\Omega^*_c \otimes \fh)$ is a module over $\Omega^* \otimes \fg$.
\end{thm}

\owen{I think we could (and maybe should) also discuss the $\EE_n$-Koszul dual situation involving cochains.}

@@

Our proof involves explicit manipulations with cochain complexes and the poset of opens in~$\RR^n$.
To connect that setting with the abstract $\infty$-categorical setting above,
we leverage deep, prior work:
\begin{itemize}
\item Lurie \cite{LurieHA} explains why the $\infty$-category of $\EE_n$ algebras is equivalent to the homotopy-coherent version of locally constant prefactorization algebras on $\RR^n$.  
In fact, he simplifies the situation a bit more. 
Let $\Disk_n^\sqcup$ denote the colored operad whose colors are balls in $\RR^n$ and whose spaces of operations are either empty or a point, depending on whether the input balls are pairwise disjoint and subsets of the output ball. 
One can work with locally constant, homotopy-coherent $\Disk_n^\sqcup$-algebras.
\item Knudsen verifies that we can model the enveloping $\EE_n$ algebra by the factorization algebra $\bU_n \fg$ described earlier.
\item Francis and Lurie give a characterization of the centralizer ${\frak Z}_n(f)$ of any $\EE_n$ algebra map $\phi: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_\phi$, where $B_\phi$ denotes $B$ viewed as a left module via the map~$\phi$.
\item In combination, the centralizer is characterized up to quasi-isomorphism, 
since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
\end{itemize}
In \S2 we review these results in more detail with an emphasis on what we need for our central theorem.

Here is an outline of our proof:
\begin{enumerate}
\item Let ${\bf f}: \cliels(\Omega_c^* \otimes \fg) \to \cliels(\Omega_c^* \otimes \fh)$ denote a map of factorization algebras that models with map $\UU_n f$ between enveloping algebras. 
We use it to produce an explicit factorization algebra $\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
\item We show this object fits canonically into a centralizer diagram: there is a map of factorization algebras
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \otimes \bU_n \fg \to \cliels(\Omega_c^* \otimes \fh)
\]
such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~${\bf f}$.
Fitting into such a diagram guarantees a canonical map 
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \to \bZ_n({\bf f})
\]
as factorization algebras, where $\bZ({\bf f})$ is some factorization algebra modeling the centralizer~${\frak Z}_n(f)$. 
\item We then verify that this map is a quasi-isomorphism on disks, by the Francis-Lurie result mentioned above. 
\end{enumerate}
Hence it induces a weak equivalence of the associated factorization algebras and hence as $\EE_n$ algebras.

@@

\begin{cor}
\label{thm: center}
The center ${\frak Z}_n(\fg)$ of the enveloping $\EE_n$ algebra $\UU_n\fg$ is the $\EE_n$ algebra $\clies(\fg, \UU_n\fg)$. 
When $k$ is $\RR$ or $\CC$, the 
center is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR^n$.
\end{cor}

@@

If $\epsilon: \fg \to 0$ is the trivial map, then we obtain the canonical augmentation $\epsilon: \UU_n \fg \to k$ of $\EE_n$ algebras.
In this case, we obtain a version of Koszul duality as the corollary.

\begin{cor}
\label{thm: koszul duality}
The centralizer of the augmentation $\epsilon: \UU_n \fg \to k$ is equivalent to $\clies(\fg)$ viewed as an $\EE_n$ algebra. It is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(V))
\]
to each open set $V \subset \RR^n$.
\end{cor}

\owen{Some easy but important situations to examine:}
\begin{itemize}
\item When $n=0$, we see naive endomorphisms arise.
\item When $n=1$, we recover standard Koszul duality and Hochschild cohomology examples.
\item When $n=1$, unpack in detail how the convolution picture matches the classic view of Koszul duality for associative (co)algebras.
\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $\EE_n$ HKR theorem.
\item Compare with $\EE_n$ HKR theorem for $\clies(\fg)$ via $\EE_n$ Koszul duality.
\item Use these facts to compute factorization homology of centralizers on manifolds with boundary --- kind of like Chern-Simons states!
\end{itemize}

Having an explicit presentation for the centralizer of a map of $\EE_n$ algebras leads to a calculation of factorization homology.
The enveloping $\EE_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebra in the sense of~\cite{AF},
and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
Therefore, for a closed $n$-dimensional manifold $M$, one has
\[
\int_M {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^*(M), \cliels( \fh \otimes \Omega^*(M))).
\]
Since $\Omega^*(S^n) \simeq \CC[\epsilon_n]$, where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$, we have
\[
\int_{S^n} {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg[\epsilon_n], \cliels( \fh[\epsilon_n]))
\]
For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
see Example~\ref{eg: TT}.

\greg{Somewhere we should recall that $\UU_n$ and its center are unoriented $\EE_n$-algebras and define factorization algebras over any manifold that came from the formula}

@@

\subsection{Recollections on $\EE_n$ algebras and prefactorization algebras}
\label{sec: en background}

@@

\begin{thm}
\label{thm:lurie1} 
There is an equivalence of $\infty$-categories between $\EE_n$-algebras and locally constant prefactorization algebras on~$\RR^n$. 
\end{thm}

@@

\subsection{Enveloping $\EE_n$ algebras of Lie algebras}
\label{sec: enveloping}

Although \cite{Knudsen} develops an adjunction between Lie and $\EE_n$ algebras \mahmoud{non-unital?}\greg{Both I think}\owen{augmented is probably best for us}
in any presentable symmetric monoidal stable $\infty$-category $\cC$,
we only work in the $\infty$-category of chain complexes $(\Mod_k, \otimes_k)$, 
where $k$ is a field of characteristic zero.
We summarize Knudsen's result in this setting as follows.

\begin{thm}\label{T:UnofLie}
There is a commuting square of adjunctions
\[
\begin{tikzcd}
\Alg_\Lie(\Mod_k) \arrow[r, bend left=20, shift left=.5ex,"\UU_n"] \arrow[dd] & \Alg_{\EE_n}(\Mod_k) \arrow[l, shift left=.5ex, "\oblv_n"] \arrow[dd]\\
&\\
\Mod_k \arrow[r, bend left=20, shift left=.5ex, "\Sigma^{1-n}"] \arrow[uu, bend left=20, shift left=.5ex, "\Free_\Lie"] & \Mod_k \arrow[l, shift left=.5ex,"\Sigma^{n-1}"] \arrow[uu, bend right=20, shift right=.5ex, "\Free_{\EE_n}"']
\end{tikzcd}
\]
\greg{Also explains what commutatrive means here ? Meaning the curved arrow diagram and the straight arrow diagram only; not combos of such}
\mahmoud{explain what oblv stands for}
where $\Sigma$ denotes suspension \owen{because tikzcd does weird things with ``[1-n]'' instead}, \mahmoud{earlier we denoted the shift by [n]. should we use $\Sigma^n$ everywhere?}.
(Curving arrows denote left adjoints.)

When $k$ is $\RR$ or $\CC$, 
the enveloping $\EE_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra $\bU_n \fg$ that assigns
\[
\bU_n \fg(V) = \cliels(\Omega^\bu_c(V) \otimes \fg)
\]
to each open set $V \subset \RR^n$.
\end{thm}

@@

\begin{rmk}
It follows from theorem~\ref{T:UnofLie} that for any $\EE_n$-algebra $B$, 
its underlying complex is equipped with a homotopy-coherent Lie algebra structure.
Depending on one's preferences, one can work with an an $L_\infty$-algebra structure or strictify to a dg Lie algebra structure (at the cost of replacing the complex with something quasi-isomorphic but typically much larger).
\end{rmk}

\subsection{Centralizers of maps of $\EE_n$ algebras and the derived center}
\label{sec: centralizer}

@@

\begin{dfn}\label{D:centralizer}
For a map $f: A \to B$ of $\EE_n$ algebras in $\cC$, 
the {\em centralizer} ${\frak Z}_n(f)$ is the $\EE_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
\[
\begin{tikzcd}
& {\frak Z}_n(f) \otimes A \arrow[dr] & \\
A \arrow[ur, "u \otimes \id"] \arrow[rr, "f"] && B
\end{tikzcd}
\]
where the arrow in the upper left is the tensor product of the unit map $u: 1_\cC \to {\frak Z}_n(f)$ and the identity map $\id: A \to A$.
The {\em center} of an $\EE_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. 
We  denote it ${\frak Z}_n(A) := {\frak Z}_n(\id_A)$.
\end{dfn}

@@

\begin{prp}
\label{T:centralizer=inthom} 
The centralizer ${\frak Z}_n(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{\EE_n}_A(\cC)$. \mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
\end{prp}

@@

\begin{prp}
\label{P:ModentoModSn}
Let $\cC^\otimes$ be a presentable symmetric monoidal stable $\infty$-category whose tensor product preserves colimits in each variable separately.
For $A$ be an $\EE_n$ algebra in $\cC$,
the $\infty$-category $\Mod^{\EE_n}_A(\cC)$ is equivalent to the $\infty$-category $\LMod_{{\int_{S^{n-1}} A}}(\cC)$.
\end{prp}

See Remark 7.3.5.3 of \cite{LurieHA}, Corollary 13 in~\cite{GG-Notes} and Section 2 of \cite{FrancisHH}.
Concretely, this claim arises from the fact that as a module over $A$ as an $\EE_n$ algebra, 
$M \in \Mod^{\EE_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}\cong S^{n-1} \times \RR_{>0}$.
This action factors through the left action of the $E_1$ algebra $\int_{S^{n-1} \times \RR_{>0}} A$ arising from factorization homology over the complement of the origin,
which integrates all those actions and through which they all factor. 
As shown in Theorem 7.5.3.1 of \cite{LurieHA} and earlier in Proposition 3.16 of \cite{FrancisHH}, 
this algebra $\int_{S^{n-1} \times \RR} A$ is equivalent to ${\rm Free}(1_\cC)$, 
the image of the unit object $1_\cC \in \cC$ under the left adjoint ${\rm Free}$ to the forgetful functor $\Mod^{\EE_n}_A(\cC) \to \cC$.

@@

\owen{Comment on notations:}
As we work in the setting of factorization algebras on $\RR^n$, 
we will use bold font to indicate such factorization models for $\EE_n$ algebra statements.
For instance, we use $\bU_n \fg$ for the factorization model of the enveloping $\EE_n$ algebra,
and we use ${\bf f}: \bU_n \fg \to \bU_n \fh$ for the factorization model of the map $f: \UU_n \fg \to \UU_n \fh$ of $\EE_n$ algebras.

@@

\owen{Probably need to mention somewhere that it's better to work with $\clies(\fg)$ as a completed object.}

@@

\subsection{Abelian Lie algebras and an $\EE_n$ HKR theorem}

>>>>

Recently, a generalization of the concept of the enveloping algebra of a Lie algebra has emerged: 
each dg Lie algebra $\fg$ has an enveloping $E_n$ algebra $\UU_n\fg$, for every $n$, 
so that $\UU_1\fg$ is the usual enveloping algebra $U\fg$. 
Building on prior work \cite{BD, AF} [Owen's thesis?], 
Knudsen \cite{Knudsen} developed these ideas extensively and offered a useful factorization algebra model for the enveloping $E_n$ algebra. 
Our central goal here is to generalize the some well-known results about the enveloping algebra $U\fg$ to $\UU_n\fg$, for all $n$, such as
\begin{enumerate}
\item[(1)] the (underived) center of $U\sl_{N+1}$ is isomorphic to $(\Sym(\CC^{N}))^{S_N}$, where $\CC^{N}$ denotes the Cartan subalgebra of $\sl_{N+1}$ and $S_N$ is the Weyl group of $SL_{N+1}$, and
\item[(2)] the derived center of the enveloping algebra $U\fg$ is given by derived invariants of the adjoint action of $\fg$ on $U\fg$. That is to say $\Hoch^*(U\fg,U\fg) \simeq \clies(\fg, U\fg)$.
\end{enumerate}
\owen{And keep going}
%
%Our results pertains to (1) by taking $N \to \infty$, and to (2) through the derived {\em centralizer} of the map $\UU_n\sl_\infty \hookrightarrow \UU_n\gl_\infty(A)$, where $A$ is a dg algebra. Note that the usual derived center is the centralizer of the identity map $\UU_n\fg \to \UU_n\fg$.
%
%We will review these notions and describe our results in detail Min the next section. When $n=1$,  \owen{state the classical thing here!}
%
%Our primary tool here is the Loday-Quillen-Tsygan (LQT) theorem which describes the large $N$ limit of the Lie algebra homology of $\gl_N(A)$, for a dg associative algebra $A$. Since the enveloping $E_n$ algebra of a Lie algebra can be constructed as a locally constant factorization algebra made out of the shifted Chevalley-Eilenberg chains \cite{}, the relevance of the LQT theorem in this context  should be apparent. From this point of view, one can think of our main result as an $E_n$ generalization of the LQT theorem. We hope these ideas have exciting applications in quantum field theory and random matrix theory, as well as to other large $N$ limit phenomena.

@@

See section~\ref{sec: en background} for a brief discussion of $E_n$ algebras and their relationship with locally constant factorization algebras on $\RR^n$, section~\ref{sec: enveloping} for a brief discussion of the enveloping $E_n$ algebra construction, and see section~\ref{sec: centralizer} 
for a brief discussion about centralizers to maps of $E_n$ algebras.

@@

Even to state our central result, we need to review a few results and terminology.
First, our basic context is $E_n$ algebras.
By $E_n$ we mean any operad or colored operad or $\infty$-operad equivalent to the topological operad of little $n$-disks in $\RR^n$, where the notion of equivalence is in some appropriate $\infty$-categorical setting of operads. 
In particular, we will require that its $\infty$-category of algebras in $\Ch_k^{\otimes_k}$ agree with those of the little $n$-disks operad. 
For us the preferred presentation is by locally constant factorization algebras on $\RR^n$,
which, as we explain below, can be understood via a colored operad whose colors are open sets in~$\RR^n$.

Many notions from ordinary algebra admit natural generalizations to $E_n$ algebras.
For instance, to each Lie algebra $\fg$ (and more generally $L_\infty$ algebra),
there is an {\em enveloping $E_n$ algebra} $\UU_n \fg$, thanks to \cite{Knudsen}.
Similarly, every $E_n$ algebra $A$ has a {\em center} ${\frak Z}_n(A)$, which is an $E_{n+1}$ algebra and hence more commutative than~$A$.
More generally, for any map of $E_n$ algebras $f: A \to B$, there is a {\em centralizer} ${\frak Z}_n(f)$, 
which is a generalization of the commutant.
We review these notions more fully in Section~\ref{sec: background}.

Our work here relies on a concrete and convenient model for these enveloping $E_n$ algebras by factorization algebras.
In particular, thanks again to \cite{Knudsen}, 
we know that the $E_n$ enveloping algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
There is another factorization algebra whose underlying assigns $\clies(\Omega^*(V) \otimes \fg)$ to each open~$V$.
Our paper shows that such factorization algebras model other important $E_n$ algebras, notably centralizers.

\begin{thm}
\label{thm: centralizer}
Let $\fg$ and $\fh$ be $L_\infty$ algebras over the real or complex numbers, 
and let $f: \fg \rightsquigarrow \fh$ be a homotopy-coherent morphism of $L_\infty$ algebras
(i.e., a map of conilpotent cocommutative coalgebras $f: \cliels(\fg) \to \cliels(\fh)$).
This map determines functorially a map of $E_n$ algebras
\[
\UU_n f: \UU_n \fg \to \UU_n \fh
\]
between their enveloping $E_n$ algebras.
The centralizer of this map ${\frak Z}_n(\UU_n f)$ is an $E_n$-algebra modeled by the factorization algebra 
\[
\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh)_f)
\]
equipped with a convolution-type product,
where the subscript $f$ indicates how $\cliels(\Omega^*_c \otimes \fh)$ is a module over $\Omega^* \otimes \fg$.
\end{thm}

\owen{I think we could (and maybe should) also discuss the $E_n$-Koszul dual situation involving cochains.}

@@

Our proof involves explicit manipulations with cochain complexes and the poset of opens in~$\RR^n$.
To connect that setting with the abstract $\infty$-categorical setting above,
we leverage deep, prior work:
\begin{itemize}
\item Lurie \cite{LurieHA} explains why the $\infty$-category of $E_n$ algebras is equivalent to the homotopy-coherent version of locally constant prefactorization algebras on $\RR^n$.  
In fact, he simplifies the situation a bit more. 
Let $\Disk_n^\sqcup$ denote the colored operad whose colors are balls in $\RR^n$ and whose spaces of operations are either empty or a point, depending on whether the input balls are pairwise disjoint and subsets of the output ball. 
One can work with locally constant, homotopy-coherent $\Disk_n^\sqcup$-algebras.
\item Knudsen verifies that we can model the enveloping $E_n$ algebra by the factorization algebra $\bU_n \fg$ described earlier.
\item Francis and Lurie give a characterization of the centralizer ${\frak Z}_n(f)$ of any $E_n$ algebra map $\phi: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_\phi$, where $B_\phi$ denotes $B$ viewed as a left module via the map~$\phi$.
\item In combination, the centralizer is characterized up to quasi-isomorphism, 
since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
\end{itemize}
In \S2 we review these results in more detail with an emphasis on what we need for our central theorem.

Here is an outline of our proof:
\begin{enumerate}
\item Let ${\bf f}: \cliels(\Omega_c^* \otimes \fg) \to \cliels(\Omega_c^* \otimes \fh)$ denote a map of factorization algebras that models with map $\UU_n f$ between enveloping algebras. 
We use it to produce an explicit factorization algebra $\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
\item We show this object fits canonically into a centralizer diagram: there is a map of factorization algebras
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \otimes \bU_n \fg \to \cliels(\Omega_c^* \otimes \fh)
\]
such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~${\bf f}$.
Fitting into such a diagram guarantees a canonical map 
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \to \bZ_n({\bf f})
\]
as factorization algebras, where $\bZ({\bf f})$ is some factorization algebra modeling the centralizer~${\frak Z}_n(f)$. 
\item We then verify that this map is a quasi-isomorphism on disks, by the Francis-Lurie result mentioned above. 
\end{enumerate}
Hence it induces a weak equivalence of the associated factorization algebras and hence as $E_n$ algebras.

@@

\begin{cor}
\label{thm: center}
The center ${\frak Z}_n(\fg)$ of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$. 
When $k$ is $\RR$ or $\CC$, the 
center is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR^n$.
\end{cor}

@@

If $\epsilon: \fg \to 0$ is the trivial map, then we obtain the canonical augmentation $\epsilon: \UU_n \fg \to k$ of $E_n$ algebras.
In this case, we obtain a version of Koszul duality as the corollary.

\begin{cor}
\label{thm: koszul duality}
The centralizer of the augmentation $\epsilon: \UU_n \fg \to k$ is equivalent to $\clies(\fg)$ viewed as an $E_n$ algebra. It is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(V))
\]
to each open set $V \subset \RR^n$.
\end{cor}

\owen{Some easy but important situations to examine:}
\begin{itemize}
\item When $n=0$, we see naive endomorphisms arise.
\item When $n=1$, we recover standard Koszul duality and Hochschild cohomology examples.
\item When $n=1$, unpack in detail how the convolution picture matches the classic view of Koszul duality for associative (co)algebras.
\item Consider $\fg$ {\em abelian} for arbitrary $n$ and compare to the $E_n$ HKR theorem.
\item Compare with $E_n$ HKR theorem for $\clies(\fg)$ via $E_n$ Koszul duality.
\item Use these facts to compute factorization homology of centralizers on manifolds with boundary --- kind of like Chern-Simons states!
\end{itemize}

Having an explicit presentation for the centralizer of a map of $E_n$ algebras leads to a calculation of factorization homology.
The enveloping $E_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebra in the sense of~\cite{AF},
and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
Therefore, for a closed $n$-dimensional manifold $M$, one has
\[
\int_M {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^*(M), \cliels( \fh \otimes \Omega^*(M))).
\]
Since $\Omega^*(S^n) \simeq \CC[\epsilon_n]$, where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$, we have
\[
\int_{S^n} {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg[\epsilon_n], \cliels( \fh[\epsilon_n]))
\]
For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
see Example~\ref{eg: TT}.

\greg{Somewhere we should recall that $\UU_n$ and its center are unoriented $E_n$-algebras and define factorization algebras over any manifold that came from the formula}

@@

\subsection{Recollections on $E_n$ algebras and prefactorization algebras}
\label{sec: en background}

@@

\begin{thm}
\label{thm:lurie1} 
There is an equivalence of $\infty$-categories between $E_n$-algebras and locally constant prefactorization algebras on~$\RR^n$. 
\end{thm}

@@

\subsection{Enveloping $E_n$ algebras of Lie algebras}
\label{sec: enveloping}

Although \cite{Knudsen} develops an adjunction between Lie and $E_n$ algebras \mahmoud{non-unital?}\greg{Both I think}\owen{augmented is probably best for us}
in any presentable symmetric monoidal stable $\infty$-category $\cC$,
we only work in the infinity category of chain complexes $(\Mod_k, \otimes_k)$, where $k$ is a field of characteristic zero.
We summarize Knudsen's result in this setting as follows.

\begin{thm}\label{T:UnofLie}
There is a commuting square of adjunctions
\[
\begin{tikzcd}
\Alg_\Lie(\Mod_k) \arrow[r, bend left=20, shift left=.5ex,"\UU_n"] \arrow[dd] & \Alg_{E_n}(\Mod_k) \arrow[l, shift left=.5ex, "\oblv_n"] \arrow[dd]\\
&\\
\Mod_k \arrow[r, bend left=20, shift left=.5ex, "\Sigma^{1-n}"] \arrow[uu, bend left=20, shift left=.5ex, "\Free_\Lie"] & \Mod_k \arrow[l, shift left=.5ex,"\Sigma^{n-1}"] \arrow[uu, bend right=20, shift right=.5ex, "\Free_{E_n}"']
\end{tikzcd}
\]
\greg{Also explains what commutatrive means here ? Meaning the curved arrow diagram and the straight arrow diagram only; not combos of such}
\mahmoud{explain what oblv stands for}
where $\Sigma$ denotes suspension \owen{because tikzcd does weird things with ``[1-n]'' instead}, \mahmoud{earlier we denoted the shift by [n]. should we use $\Sigma^n$ everywhere?}.
(Curving arrows denote left adjoints.)

When $k$ is $\RR$ or $\CC$, 
the enveloping $E_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra $\bU_n \fg$ that assigns
\[
\bU_n \fg(V) = \cliels(\Omega^\bu_c(V) \otimes \fg)
\]
to each open set $V \subset \RR^n$.
\end{thm}

@@

\begin{rmk}
It follows from theorem~\ref{T:UnofLie} that for any $E_n$-algebra $B$, 
its underlying complex is equipped with a homotopy-coherent Lie algebra structure.
Depending on one's preferences, one can work with an an $L_\infty$-algebra structure or strictify to a dg Lie algebra structure (at the cost of replacing the complex with something quasi-isomorphic but typically much larger).
\end{rmk}

\subsection{Centralizers of maps of $E_n$ algebras and the derived center}
\label{sec: centralizer}

@@

\begin{dfn}\label{D:centralizer}
For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
the {\em centralizer} ${\frak Z}_n(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
\[
\begin{tikzcd}
& {\frak Z}_n(f) \otimes A \arrow[dr] & \\
A \arrow[ur, "u \otimes \id"] \arrow[rr, "f"] && B
\end{tikzcd}
\]
where the arrow in the upper left is the tensor product of the unit map $u: 1_\cC \to {\frak Z}_n(f)$ and the identity map $\id: A \to A$.
The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. 
We  denote it ${\frak Z}_n(A) := {\frak Z}_n(\id_A)$.
\end{dfn}

@@

\begin{prp}
\label{T:centralizer=inthom} 
The centralizer ${\frak Z}_n(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$. \mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
\end{prp}

@@

\begin{prp}
\label{P:ModentoModSn}
Let $\cC^\otimes$ be a presentable symmetric monoidal stable $\infty$-category whose tensor product preserves colimits in each variable separately.
For $A$ be an $E_n$ algebra in $\cC$,
the $\infty$-category $\Mod^{E_n}_A(\cC)$ is equivalent to the $\infty$-category $\LMod_{{\int_{S^{n-1}} A}}(\cC)$.
\end{prp}

See Remark 7.3.5.3 of \cite{LurieHA}, Corollary 13 in~\cite{GG-Notes} and Section 2 of \cite{FrancisHH}.
Concretely, this claim arises from the fact that as a module over $A$ as an $E_n$ algebra, 
$M \in \Mod^{E_n}_A(\cC)$ is equipped with a commuting family of actions by $A$ parametrized by $\RR^n \setminus \{0\}\cong S^{n-1} \times \RR_{>0}$.
This action factors through the left action of the $E_1$ algebra $\int_{S^{n-1} \times \RR_{>0}} A$ arising from factorization homology over the complement of the origin,
which integrates all those actions and through which they all factor. 
As shown in Theorem 7.5.3.1 of \cite{LurieHA} and earlier in Proposition 3.16 of \cite{FrancisHH}, 
this algebra $\int_{S^{n-1} \times \RR} A$ is equivalent to ${\rm Free}(1_\cC)$, 
the image of the unit object $1_\cC \in \cC$ under the left adjoint ${\rm Free}$ to the forgetful functor $\Mod^{E_n}_A(\cC) \to \cC$.

@@

\owen{Comment on notations:}
As we work in the setting of factorization algebras on $\RR^n$, 
we will use bold font to indicate such factorization models for $E_n$ algebra statements.
For instance, we use $\bU_n \fg$ for the factorization model of the enveloping $E_n$ algebra,
and we use ${\bf f}: \bU_n \fg \to \bU_n \fh$ for the factorization model of the map $f: \UU_n \fg \to \UU_n \fh$ of $E_n$ algebras.

@@

@@

\subsection{Abelian Lie algebras and an $E_n$ HKR theorem}

Given a free dg commutative algebra $A = \Sym(V^\bullet)$ generated by a cochain complex $V^\bullet$,
one can view it as an $E_n$ algebra via the forgetful functor determined by the operad map $E_n \to E_\infty$.
We will blithely view any commutative algebra as an $E_n$ algebra for any $n$ via this forgetting.
